Towards End-user Web Scraping For Customization

### 2021-04-09 paper.tex
Removed ads from demo screenshots and added acknoledgements section
Removed reference to web version from PDF

This paper is directed at publication. We have provided a PDF but it is best viewed in the online version (\href{https://kapaya.github.io/px21/}{kapaya.github.io/px21}) which includes videos demonstrating the system.

@@

>>>>

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software
Design Group, the anonymous reviewers of PX/21 and the particpants of
PX/21 for providing valuable feedback on this work.
